Meta-analysis for the Effect of SSRIs on Anxiety

### 2023-01-23 manuscript/manuscript.Rmd
Analysis with more iterations

---
title: "Untitled"
output: bookdown::html_document2
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

@@

zscores <- scale(dat[["yi"]])
maxz <- max(abs(zscores))
if(maxz > 3.3) stop("Potential outlier in Y-space")
saveRDS(dat, "dat.RData")
```

@@

```{r, eval = run_everything}
refcats <- read.csv("../reference_categories.csv", stringsAsFactors = FALSE)
modres <- lapply(samples, function(p){
  df <- dat[dat$Sample == p, ]
  mods_cont <- mods[!mods %in% cat]

@@

  # Find ref cat
  catvars <- sapply(dfmod, class) == "factor"
  dfmod[catvars] <- lapply(dfmod[catvars], function(v){
    tab <- table(v)
    relevel(v, ref = names(tab)[which.max(tab)])
  })
  # refcat <- data.frame(do.call(rbind,lapply(names(dfmod[catvars]), function(n){c(n, levels(dfmod[[n]])[1])})))
  refcat <- data.frame(Variable = names(refcats)[-1],
                       Reference = unlist(refcats[refcats$sample == p, -1]))
  refcat <- refcat[refcat$Variable %in% names(dfmod[catvars]), ]
  if(nrow(refcat) > 0) names(refcat) <- c("Variable", "Reference")
  completecases <- complete.cases(dfmod)
  modmat <- model.matrix(~., dfmod)

@@

  standardize <- list(
    center = c(attr(std,"scaled:center"), rep(0, ncol(df_cats))),
    scale = c(attr(std,"scaled:scale"), rep(1, ncol(df_cats)))
  )
  moddat <- cbind(yi = yi_notcentered, vi = df$vi[completecases], std, df_cats)
  moddat$study <- df$id_experiment[completecases]
  pma <- brma(yi ~., study = "study", data = moddat, standardize = standardize)
  saveRDS(pma, paste0("pma_", p, ".RData"))
  sumpma <- data.frame(summary(pma)$coefficients)
  sumpma <- cbind(rownames(sumpma), sumpma)
  names(sumpma)[1:3] <- c("Parameter", "Estimate", "se")
  sumpma <- sumpma[!sumpma$Parameter == "tau", ]
  rownames(sumpma) <- NULL
  sumpma$CI <- conf_int(lb = sumpma$X2.5., ub = sumpma$X97.5.)
  pstars <- c("*", "")[as.integer(apply(sumpma[, c("X2.5.", 
                                                   "X97.5.")], 1, function(x) {
                                                     sum(sign(x)) == 0
                                                   })) + 1]
  sumpma$p <- pstars
  sumpma[c("sd", grep("^X", names(sumpma), value = T))] <- NULL
  write.csv(sumpma, paste0("brma_mods_", p, ".csv"))

>>>>

---
title: "Meta-analysis for the Effect of SSRIs on Anxiety"
output: bookdown::html_document2
date: '`r format(Sys.time(), "%d %B, %Y")`'
bibliography: references.bib
knit: worcs::cite_all
---

@@

zscores <- scale(dat[["yi"]])
maxz <- max(abs(zscores))
#if(maxz > 3.3) stop("Potential outlier in Y-space")
#dat <- dat[!abs(zscores) > 3.3, ]
saveRDS(dat, "dat.RData")
```

@@

```{r, eval = run_everything}
# Refcats now provided in different format
refcats <- read.csv("../reference_categories.csv", stringsAsFactors = FALSE)
refcats <- lapply(samples, function(s){
    out <- refcats[refcats$sample == s, -1]
    data.frame(Variable = names(out),
                      Reference = unlist(out))
})
names(refcats) <- samples
modres <- lapply(samples, function(p){
  df <- dat[dat$Sample == p, ]
  mods_cont <- mods[!mods %in% cat]

@@

  # Find ref cat
  # Changed, because reference categories are now provided by researchers
  catvars <- sapply(dfmod, class) == "factor"
  catvars <- names(catvars)[catvars]
  refcat <- as.data.frame(refcats[[p]])
  dfmod[catvars] <- lapply(catvars, function(c){
    v <- dfmod[[c]]
    relevel(v, ref = refcat$Reference[match(tolower(c), refcat$Variable)])
  })
  completecases <- complete.cases(dfmod)
  modmat <- model.matrix(~., dfmod)

@@

  standardize <- list(
    center = c(attr(std,"scaled:center"), rep(0, ncol(df_cats))),
    scale = c(attr(std,"scaled:scale"), rep(1, ncol(df_cats)))
  )
  moddat <- cbind(yi = yi_notcentered, vi = df$vi[completecases], std, df_cats)
  moddat$study <- df$id_experiment[completecases]
  pma <- brma(yi ~., study = "study", data = moddat, standardize = standardize, iter = 10000)
  saveRDS(pma, paste0("pma_", p, ".RData"))
  sumpma <- data.frame(summary(pma)$coefficients)
  sumpma <- cbind(rownames(sumpma), sumpma)
  names(sumpma)[1:3] <- c("Parameter", "Estimate", "se")
  sumpma <- sumpma[!sumpma$Parameter == "tau", ]
  rownames(sumpma) <- NULL
  sumpma$CI <- conf_int(lb = sumpma$X2.5., ub = sumpma$X97.5.)
  pstars <- c("*", "")[as.integer(apply(sumpma[, c("X2.5.", 
                                                   "X97.5.")], 1, function(x) {
                                                     sum(sign(x)) == 0
                                                   })) + 1]
  sumpma$p <- pstars
  sumpma[c("sd", grep("^X", names(sumpma), value = T))] <- NULL
  write.csv(sumpma, paste0("brma_mods_", p, ".csv"))
